---
title: "Final Project Code Supplement"
author: "Kenta Hikino, Avery Watts, Rebecca Flowers"
date: "2022-11-16"
output: pdf_document
---

```{r setup, include=FALSE, warning=FALSE}
# Load the required R packages in this setup chunk
library(ggformula)
library(car)
library(dplyr)
library(mosaic)
library(GGally)
library(effects)
library(broom)
library(rms)
```

## Initial Exploratory Data Analysis
Theory: 

Theoretical Model Equation:
$logit(\pi) = \beta_0 + \beta_1x_{timesMoved} + \beta_2x_{drugsAtHome} - \beta_3x_{talkAtHome} - \beta_4x^2_{rulesAtHome}$

```{r Data cleaning, warning=FALSE}
# Load the data sets in the set up chunk
insurance <- read.csv("~/stat230/insurance.csv")

insurance <- insurance[complete.cases(insurance),]

#insurance <- insurance %>%
  #filter(charges < 10000)
```

$\mu[MedicalCosts|age, sex, bmi, children, smoker, region] = \beta_0 + log(\beta_1x_{age}) + \beta_2x_{sex} + log(\beta_3x_{bmi}) + log(\beta_4x_{children}) + \beta_5x_{smoker} + \beta_6x_{NWRegion} + \beta_7x_{SERegion} + \beta_8x_{SWRegion}$

## Preliminary Model
```{r}
prelim_model <- lm(log(charges) ~ log(age) + sex + log(bmi) + log(children + 1) + smoker + region, data = insurance)
summary(prelim_model)

# Visualize relationships
ggpairs(insurance, columns = c("charges", "age", "sex", "bmi", "children", 
                        "smoker", "region"))

model_resid <- resid(prelim_model)

# Constant error variance test: Signs of heteroscedasticity in some variables,
# log of age and fitted values plots showed patterns of wedging, which violates assumptions
residualPlots(prelim_model, tests = FALSE, quadratic = FALSE)

# Test of Normality, The assumption was not met, we need more data with more 
# explanatory variables
histogram(insurance$charges, breaks = 100)
gf_qq(~model_resid, ylab = "Residual", fig.height = 2.5, fig.width = 4) %>%
  gf_qqline(~model_resid)

# Test of Multicollinearity, everything is under 5, looks good
vif(prelim_model)

# Independence: We assume that the observations were selected independently and
# randomly from the population.

# View Influence of Outliers, outliers were flagged, will be removed
infIndexPlot(prelim_model, vars = "cook")
```


## T-test, significance tests, and Final model Assessments
```{r Model Analysis}
# Wald's test
summary(prelim_model)

avPlots(prelim_model)
```


